They're Clutching up! Team Momentum in Round-Based Esports

### 2022-08-19 paper/paper.tex
ALL THE SYMBOL CHANGES

There have been a handful of studies of the distribution of games played
in a series of a professional sport. Most assume a constant probability
\(p\) of a given team winning a game in the series, regardless of the
series state. Mosteller (1952) observed that the American League had
dominated the National League in Major League Baseball's (MLB) World
Series matchups, implying that matchups should not modeled with
\(p = 0.5\). Mosteller proposed three approaches for identifying the
optimal constant probability value of the stronger team in the World
Series, finding \(p \approx 0.65\). in each case: (1) solving for \(p\)
from the empirical average number of games won by the loser of the
series, which he called the ``method of moments'' approach; (2)
maximizing the likelihood that the sample would have been drawn from a
population in which the probability of a team winning a game is constant
across the series (i.e.~maximum likelihood), and (3) minimizing the
chi-square goodness of fit statistic for \(p\).

Chance (2020) re-examines the constant probability notion in Major
League Baseball's World Series (1923--2018), the National Basketball
Association's Finals (1951--2018), and the National Hockey League's
Stanley Cup (1939--2018). Chance finds strong evidence against the null
hypothesis of \(p = 0.5\) in the MLB and NHL championship series when
applying Mosteller's first and second methods.{[}\^{}8{]} {[}\^{}8{]}:
Chance goes on to outline a conditional probability framework
(likelihood of winning a game given the series state) which can exactly
explain the distribution of the number of games played.

@@

Studying both player streaks and team streaks in basketball, in both
observational and controlled settings. Gilovich et al. (1985) do not
find evidence for the hot hand phenomenon. However, Miller and Sanjurjo
(2018) refuted the conclusions of Gilovich et al., proving a framework
for quantifying streak selection bias, which effectively works in the
manner posited by the gambler's fallacy\footnote{Streak selection bias,
  ``in conjunction with a quasi-Bayesian model of decision making under
  sample size neglect\ldots{} provides a novel structural candidate
  explanationfor the persistence of gambler's fallacy beliefs'', per
  Miller and Sanjurjo (2018).}. Specifically, Miller and Sanjurjo say
that a ``bias exists in a common measure of the conditional dependence
of present outcomes on streaks of past outcomes in sequential data''
implying that, under i.i.d. conditions, ``the proportion of successes
among the outcomes that immediately follow a streak of consecutive
successes is expected to be strictly less than the underlying
(conditional) probability of success''. When applying streak selection
bias to Giloveih et al.'s data, Miller and Sanjurjo come to the opposite
conclusions as Giloveih et al.

Despite the plethora of existing research on games played in a series
and momentum in sports, these topics have yet to be investigated heavily
in esports. Work has been done to examine in-round win probability in
other FPS titles such as Counter-Strike (Xenopoulos, Freeman, and Silva
2022) and Valorant (DeRover 2021), both of which are round-based like
CoD SnD. However, research on round-level trends is sparse, perhaps
because games like Counter-Strike and Valorant both have economic
aspects that can create clear advantages on side in a given round, given
how prior rounds played out.\footnote{Additionally, both Counter-Strike
  and Valorant have overtime rules and blocked offensive/defensive roles
  (i.e.~playing either offense or defense for many consecutive rounds).}

@@

The general formula for the probability \(P_E(r)\) that a best-of-\(s\)
series (\(s = 11\) for CoD SnD) lasts \(r\) rounds given constant
probability \(p\) of one team\footnote{If \(p > 0.5\), then one might
  say that this team is the better team (known in hindsight).} winning
each round is

@@

\begin{equation}\protect\hypertarget{eq:series-length}{}{
P_E(r) = \frac{(r - 1)!}{(m - 1)!(r - s)!}(p^{m}(1 - p)^{r - m} + p^{r - m}(1 - p)^m).
}\label{eq:series-length}\end{equation}

The chi-square goodness of fit statistic can be used to test the
constant found probability hypothesis for \(0 \leq p \leq 1\).

\begin{equation}\protect\hypertarget{eq:chi-squ}{}{
\chi^2 = \sum^R \frac{(P_O(r) - P_E(r))^2}{P_E(r)}
}\label{eq:chi-squ}\end{equation}

For CoD SnD, \(r \in R [6, 7, 8, 9, 10, 11]\).

@@

Without accounting for the streak selection bias described by Miller and
Sanjurjo (2018), the round win probability after a streak of \(k\) round
wins for a best-of-\(s\) series (\(s = 11\) for CoD SnD), accounting for
the series lasting \(r\) rounds known in hindsight, is

@@

The ``hindsight'' round loss probability after a streak of \(k\) round
losses for a series lasting \(r\) rounds, \(p^{l|kr}\), can be
formulated symmetrically.\footnote{Note that these probabilities are
  separate from the constant round probabilities in Sections
  \ref{sec:method-rounds-played} and \ref{sec:results-rounds-played}.}

However, as shown by Miller and Sanjurjo, we should expect the observed
proportion of rounds wins after a streak \(k\) rounds wins for a series
lasting \(r\) rounds, \(\hat{P}_{w|kr}\), to be strictly less than
\(p^{w|kr}\).

@@

Miller and Sanjurjo (2018) note that there does not exists a closed form
representation for
\(E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]\) for
\(k > 1\).

@@

First, I investigate the constant probability assumption and the
distribution of rounds played in a series. Chance's (2020) work is
closely related to mine, and, in fact, provides a guide for this
investigation.

@@

Using Equation \ref{eq:chi-squ}, \(\chi^2 = 16.0\) (p-value of 0.0068)
for a naive constant round win probability \(p_0 = 0.5\). Thus, I can
comfortably reject the constant probability null hypothesis for
\(p_0 = 0.5\), even at a confidence level of \(\alpha = 0.01\).
Afterwards, I investigate post-streak win rates, building on my
learnings from the constant probability assumption analysis. I agree
with Miller and Sanjurjo's (2018) framework for streak selection bias,
accounting for it in when analyzing momentum.

Table \ref{tbl:cod-prob-series-lasting-r-rounds} shows the expected
probabilities for \(s = 11\) under the naive assumption that
\(p_0 = 0.5\) for a given round, along with the observed proportions
\(P_O(r)\) in CoD SnD.

\begin{longtable}{rrrr}
\caption{The probabilities that a best-of-11 series lasts $r$ rounds ($P_E(r)$, where $r \in [6, 7, 8, 9, 10, 11]$) under the assumption that each team has a 50\% probability ($p_0 = 0.5$) of winning each game. The observed frequencies observed are shown as a count $N_O(r)$ and as a proportion $P_O(r)$ of all series.}\label{tbl:cod-prob-series-lasting-r-rounds} \\
\toprule
&  & \multicolumn{2}{c}{Observed} \\ 
\cmidrule(lr){3-4}
$r$ & $P_E(r)$ & $P_O(r)$ & $N_O(r)$ \\ 
\midrule
6 & $3.1\%$ & $4.7\%$ & 40 \\ 
7 & $9.4\%$ & $11.9\%$ & 101 \\ 
8 & $16.4\%$ & $16.5\%$ & 141 \\ 
9 & $21.9\%$ & $21.7\%$ & 185 \\ 
10 & $24.6\%$ & $21.5\%$ & 183 \\ 
11 & $24.6\%$ & $23.7\%$ & 202 \\ 
\bottomrule
\end{longtable}

Table \ref{tbl:mosteller-methods-results} shows the alternate values for
the constant round win probability \(p\) that I find when applying the
three methods suggested by Mosteller (1952). Each is approximately or
equal to 0.575, and, when applying Equation \ref{eq:chi-squ}, each
results in a \(\chi^2\) value for which I cannot reject the constant
probability null hypothesis.

\begin{longtable}[]{@{}lrr@{}}
\caption{Alternate estimates of the constant probability \(p\) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive \(p = 0.5\).}\label{tbl:mosteller-methods-results} \\
\toprule()
Method & \(p(r)\) & \(\chi^2\) (p-value) \\
\midrule()
\endfirsthead
\toprule()
Method & \(p(r)\) & \(\chi^2\) (p-value) \\
\midrule()
\endhead
0. Naive & 0.5000 & 16.0 (\textless=0.01) \\
1. Method of moments & 0.5725 & 3.6 (0.6) \\
2. Maximum likelihood & 0.5750 & 3.5 (0.62) \\
3. Minimum \(\chi^2\) & 0.5775 & 3.5 (0.62) \\
\bottomrule()
\end{longtable}

Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new
\(P_E(r)\) when re-applying Equation \ref{eq:series-length} for the
maximum likelihood estimate \(p_2 = 0.575\).\footnote{The method of
  moments and minimum \(\chi^2\) estimates for \(p\) are omitted simply
  because the results would be nearly identical to those for the maximum
  likelihood estimate of \(p\) (since they are all \(\approx 0.575\)).}
I observe that \(P_E(r)\) is notably larger for \(p_{2}\) when
\(r \in [6, 7]\), more closely matching \(P_O(r)\). \(p_{2}\) is also
closer to \(P_O(r)\) for \(r \in [9, 10]\), although not for
\(r \in [8, 11]\).

\begin{longtable}[]{@{}rrrr@{}}
\caption{The probabilities that a best-of-11 series lasts $r$ rounds under the naive assumption $p_0 = 0.5$ and the maximum likelihood estimation $p_2 = 0.575$.}\label{tbl:expected-series-lengths-alternative-ps} \\
\toprule()
$r$ & $p_0(r)$ = 0.5 & $p_2(r)$ = 0.575 & $P_O(r)$ \\
\midrule()
\endhead
6 & 3.1\% & 4.2\% & 4.7\% \\
7 & 9.4\% & 11.2\% & 11.9\% \\
8 & 16.4\% & 17.8\% & 16.5\% \\
9 & 21.9\% & 21.8\% & 21.7\% \\
10 & 24.6\% & 23.0\% & 21.5\% \\
11 & 24.6\% & 22.0\% & 23.7\% \\
\bottomrule()
\end{longtable}

It is fair to conclude that the constant round win probability
assumption can be valid in CoD SnD series with the appropriate choice of
\(p\) (\(\approx 0.575\)).

@@

Given that people typically perceive streaks as beginning after the
third success (or failure) at minimum (Carlson and Shu 2007), I focus on
round win percentages in rounds immediately following streaks of three
wins.\footnote{Three happens to also be a reasonable number for series
  that lasts at maximum 11 rounds.} Table
\ref{tbl:cod-round-win-prop-after-k-wins} shows
\(\hat{P}^{kr,\text{win}}_O\) and \(\hat{P}^{kr,\text{loss}}_O\) for
\(k = 3\) streaks respectively.

TODO: Put p-value in parentheses

\begin{longtable}{rrrrrrr}
\caption{First, observed proportion of wins ($\hat{P}^{kr,\text{win}}_O$) and expected proportion of wins, both un-adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$), after 3-round win streak, for a series lasting $r$ rounds. Second, observed proportion of losses ($\hat{P}^{kr,\text{loss}}_O$) and expected proportion of losses, both un-adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$), after 3-round loss streak}\label{tbl:cod-round-win-prop-after-k-wins} \\
\toprule
\multicolumn{7}{c}{\text{3 round win streak}} \\
 &  &  & \multicolumn{2}{c}{\text{Unadjusted}} & \multicolumn{2}{c}{\text{Adjusted}} \\ 
\cmidrule(lr){4-5} \cmidrule(lr){6-7}
$r$ & $N^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$ &  $p$-value & $\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$ & $p$-value \\ 
\midrule
7 & 209 & $75\%$ & $75\%$ & 0.58 & $61\%$ & <=0.01 \\ 
8 & 209 & $62\%$ & $60\%$ & 0.28 & $45\%$ & <=0.01 \\ 
9 & 193 & $52\%$ & $50\%$ & 0.33 & $35\%$ & <=0.01 \\ 
10 & 151 & $44\%$ & $43\%$ & 0.45 & $29\%$ & <=0.01 \\ 
11 & 150 & $40\%$ & $38\%$ & 0.29 & $25\%$ & <=0.01 \\ 
\toprule
\multicolumn{7}{c}{\text{3 round loss streak}} \\
 &  &  & \multicolumn{2}{c}{\text{Unadjusted}} & \multicolumn{2}{c}{\text{Adjusted}} \\ 
\cmidrule(lr){4-5} \cmidrule(lr){6-7}
$r$ & $N^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$ &  $p$-value & $\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$ & $p$-value \\ 
\midrule
10 & 60 & $13\%$ & $14\%$ & 0.64 & $10\%$ & 0.26 \\ 
11 & 129 & $24\%$ & $25\%$ & 0.63 & $16\%$ & <=0.01 \\ 
\bottomrule
\end{longtable}

@@

>>>>

There have been a handful of studies of the distribution of games played
in a series of a professional sport. Most assume a constant probability
\(\phi\) of a given team winning a game in the series, regardless of the
series state. Mosteller (1952) observed that the American League had
dominated the National League in Major League Baseball's (MLB) World
Series matchups, implying that matchups should not modeled with
\(\phi = 0.5\). Mosteller proposed three approaches for identifying the
optimal constant probability value of the stronger team in the World
Series, finding \(\phi \approx 0.65\). in each case: (1) solving for
\(p\) from the empirical average number of games won by the loser of the
series, which he called the ``method of moments'' approach; (2)
maximizing the likelihood that the sample would have been drawn from a
population in which the probability of a team winning a game is constant
across the series (i.e.~maximum likelihood), and (3) minimizing the
chi-square goodness of fit statistic for \(\phi\).

Chance (2020) re-examines the constant probability notion in Major
League Baseball's (MLB) World Series (1923--2018), the National
Basketball Association's (NBA) Finals (1951--2018), and the National
Hockey League's (NHL) Stanley Cup (1939--2018). Chance finds strong
evidence against the null hypothesis of \(\phi = 0.5\) in the MLB and
NHL championship series when applying Mosteller's first and second
methods. Chance goes on to outline a conditional probability framework
(likelihood of winning a game given the series state) which can exactly
explain the distribution of the number of games played.

@@

Studying both player streaks and team streaks in basketball, in both
observational and controlled settings. Gilovich et al. (1985),
henceforth GVT, do not find evidence for the hot hand phenomenon.
However, Miller and Sanjurjo (2018), henceforth MS, refuted the
conclusions of GVT, proving a framework for quantifying streak selection
bias, which effectively works in the manner posited by the gambler's
fallacy\footnote{Streak selection bias, ``in conjunction with a
  quasi-Bayesian model of decision making under sample size
  neglect\ldots{} provides a novel structural candidate explanation for
  the persistence of gambler's fallacy beliefs'', per MS (2018).}.
Specifically, MS say that a ``bias exists in a common measure of the
conditional dependence of present outcomes on streaks of past outcomes
in sequential data'' implying that, under i.i.d. conditions, ``the
proportion of successes among the outcomes that immediately follow a
streak of consecutive successes is expected to be strictly less than the
underlying (conditional) probability of success''. When applying streak
selection bias to GVT.'s data, MS come to the opposite conclusions as
GVT.

Despite the plethora of existing research on games played in a series
and momentum in sports, these topics have yet to be investigated heavily
in esports. Work has been done to examine in-round win probability in
other FPS titles such as Counter-Strike (Xenopoulos, Freeman, and Silva
2022) and Valorant (DeRover 2021), both of which are round-based like
CoD SnD. However, research on round-level trends is sparse, perhaps
because games like Counter-Strike and Valorant both have economic
aspects that can create clear advantages on side in a given round, given
how prior rounds played out.

Additionally, both Counter-Strike and Valorant have overtime rules and
blocked offensive/defensive roles (i.e.~playing either offense or
defense for many consecutive rounds). On the other hand, teams in CoD
SnD rotate sides every round, analogous to a 1-1-1-1-1-1-1 format for
home advantage in best-of-seven series for professional sports like the
MLB, NBA, and NHL.\footnote{1-1-1-1-1-1-1 is not used today in these
  leagues, but it was at least one in each league.} While theoretically
one might be able to account for any kind of balanced rotation, such as
a ``blocky'' on like a 5-5-1, the rotation of team sides every round is
convenient, particularly for convincing ourselves that rounds could
reasonably be modeled as i.i.d. Bernoulli trials.

@@

The formula for the expected proportion of seriesn a best-of-\(s\)
format (\(s = 11\) rounds for CoD SnD), ending in \(r\) rounds
(\(r \leq s\)), \(\hat{\Phi}(r)\), for a constant round win probability
\(\phi\) (\(0 \leq \phi \leq 1\)) for one team\footnote{If
  \(\phi > 0.5\), then one might say that this team is the better team
  (known in hindsight).} is

@@

\begin{equation}\protect\hypertarget{eq:series-length}{}{
\hat{\Phi}(r) = \frac{(r - 1)!}{(m - 1)!(r - s)!}(\phi^{m}(1 - \phi)^{r - m} + \phi^{r - m}(1 - \phi)^m).
}\label{eq:series-length}\end{equation}

To evaluate the constant round win probability hypothesis--that is, that
the expected and observed round win rates, \(\hat{\Phi}(r)\) and
\(\Phi(r)\) respectively, are equal to one another--we can compute the
chi-square goodness of fit statistic, \(\chi^2\).

\begin{equation}\protect\hypertarget{eq:chi-squ}{}{
\chi^2 = \sum^R \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)}
}\label{eq:chi-squ}\end{equation}

For CoD SnD, \(r \in R = [6, 7, 8, 9, 10, 11]\).

@@

When considering momentum in consecutive rounds wins, I use the
descriptor ``hindsight'' because I account for the length of the series
(\(r\) rounds). Without accounting for the streak selection bias
described by MS (2018), the ``hindsight'' Bernoulli round win
probability immediately following a streak of \(k\) round wins for a
best-of-\(s\) series, \(p^{w|kr}\), is

@@

The hindsight Bernoulli round loss probability after a streak of \(k\)
round wins, \(p^{l|kr}\), can be formulated symmetrically.

However, as shown by MS, we should expect the proportion of rounds wins
immediately following a streak \(k\) rounds wins for a series lasting
\(r\) rounds, \(\hat{P}^{w|kr}\), to be strictly less than
\(p^{w|kr}\).\footnote{See Appendix E.1 of MS (2018) for details on the
  proof that follows.}

@@

MS (2018) note that there does not exists a closed form representation
for \(E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]\)
(\(\hat{P}_k(\mathbf{X})\) is the analogue for \(\hat{P}^{w|kr}\) in my
CoD SnD notation), for \(k > 1\). Figure 1 shows how the expected value
varies as a function of the total number of trials \(n\), given \(p\)
and \(k > 1\).\footnote{I've adapted the code from Vafa (2017), which
  implements MS's framework (2018).}

\begin{figure}
\centering
\includegraphics{images/npkd.png}
\caption{The expected value of the proportion of successes on trials that immediately follow $k$ consecutive successes, $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$, for Bernoulli trial success $p = 0.5$ and streak lengths $k \in [2, 3, 4]$, as a function of the total number of trials $n.$}
\end{figure}

@@

First, I investigate the constant probability assumption and the
distribution of rounds played in a series. Chance's (2020) work is
closely related to mine, and, in fact, provides a guide for this
investigation. Afterwards, I investigate post-streak win rates and the
context of momentum, leveraging MS's (2018) framework for streak
selection bias.

@@

Using Equation \ref{eq:chi-squ}, I find that \(\chi^2 = 16.0\) (p-value
of 0.0068) for the naive constant round win probability
\(\phi_0 = 0.5\). Thus, I can comfortably reject the constant
probability null hypothesis for \(\phi_0 = 0.5\), even at a confidence
level of \(\alpha = 0.01\).

Table \ref{tbl:cod-prob-series-lasting-r-rounds} shows the expected
series lasting \(r\) rounds, \(\hat{\Phi}_0(r)\) (under the assumption
\(\phi_0 = 0.5\)), for \(s = 11\), along with the observed proportions,
\(\Phi(r)\), in CoD SnD.

\begin{longtable}{rrrr}
\caption{The expected proportion of series lasting $r$ rounds ($\hat{\Phi}_0(r)$) in a best-of-11 format, wehre $r \in R = [6, 7, 8, 9, 10, 11]$ under the assumption that each team has a constant round win probability $\phi_0 = 0.5$. The observed frequencies for CoD SnD are shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum^R N(r)$).}\label{tbl:cod-prob-series-lasting-r-rounds} \\
\toprule
$r$ & $\hat{\Phi}_0(r)$ & $\Phi(r)$ & $N(r)$ \\ 
\midrule
6 & $3.1\%$ & $4.7\%$ & 40 \\ 
7 & $9.4\%$ & $11.9\%$ & 101 \\ 
8 & $16.4\%$ & $16.5\%$ & 141 \\ 
9 & $21.9\%$ & $21.7\%$ & 185 \\ 
10 & $24.6\%$ & $21.5\%$ & 183 \\ 
11 & $24.6\%$ & $23.7\%$ & 202 \\ 
\bottomrule
\end{longtable}

Table \ref{tbl:mosteller-methods-results} shows the alternate values for
the constant round win probability that I find when applying the three
methods suggested by Mosteller (1952). Each is approximately or equal to
0.575, and, when applying Equation \ref{eq:chi-squ}, each results in a
\(\chi^2\) value for which I cannot reject the constant probability null
hypothesis.

\begin{longtable}[]{@{}lrr@{}}
\caption{Alternate estimates of the constant probability ($\phi$) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive ($\phi_0 = 0.5$).}\label{tbl:mosteller-methods-results} \\
\toprule()
Method & $\phi$ & $\chi^2$ (p-value) \\
\midrule()
\endfirsthead
\toprule()
Method & $\phi(r)$ & $\chi^2$ (p-value) \\
\midrule()
\endhead
0. Naive & 0.5000 & 16.0 (\textless=0.01) \\
1. Method of moments & 0.5725 & 3.6 (0.6) \\
2. Maximum likelihood & 0.5750 & 3.5 (0.62) \\
3. Minimum ($\chi^2$) & 0.5775 & 3.5 (0.62) \\
\bottomrule()
\end{longtable}

Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new
\(\hat{\Phi}(r)\) when re-applying Equation \ref{eq:series-length} for
the maximum likelihood estimate \(\phi_2 = 0.575\), resulting in a new
set of expected proportions of series lasting \(r\) rounds
\(\hat{\Phi}_2(r)\).\footnote{The method of moments and minimum
  \(\chi^2\) estimates for \(\phi\) are omitted simply because the
  results would be nearly identical to those for the maximum likelihood
  estimate of \(\phi\) (since they are all \(\approx 0.575\)).} I
observe that \(\hat{\Phi}_2(r)\) is larger than \(\hat{\Phi}_0(r)\) for
\(r \in [6, 7]\), more closely matching \(\Phi(r)\). \(\hat{\Phi}_2(r)\)
is also closer to the observed \(\Phi(r)\) for \(r \in [9, 10]\),
although not for \(r \in [8, 11]\).

\begin{longtable}[]{@{}rrrr@{}}
\caption{The observed proportion of series $\Phi(r)$ ending in $r$ rounds in CoD SnD's best-of-11 format, compared to the expected proportion $\hat{\Phi}_0(r)$ the naive assumption $\phi_0 = 0.5$ and the expected proportion $\hat{\Phi}_2(r)$ under the maximum likelihood estimate $\phi_2 = 0.575$ for constant round win probability.}\label{tbl:expected-series-lengths-alternative-ps} \\
\toprule()
$r$ & $\hat{\Phi}_0(r)$ = 0.5 & $\hat{\Phi}_2(r)$ = 0.575 & $\Phi(r)$ \\
\midrule()
\endhead
6 & 3.1\% & 4.2\% & 4.7\% \\
7 & 9.4\% & 11.2\% & 11.9\% \\
8 & 16.4\% & 17.8\% & 16.5\% \\
9 & 21.9\% & 21.8\% & 21.7\% \\
10 & 24.6\% & 23.0\% & 21.5\% \\
11 & 24.6\% & 22.0\% & 23.7\% \\
\bottomrule()
\end{longtable}

Observing that \(\hat{\Phi}_2(r)\) reasonably matches \(\Phi(r)\)
(especially in comparison to \(\hat{\Phi}_0(r)\)), along with the null
hypothesis rejection shown in Table \ref{tbl:mosteller-methods-results},
it is fair to conclude that the constant round win probability
assumption can be valid in CoD SnD series with the appropriate choice of
\(\phi\) (\(\approx 0.575\)).

@@

Given that people typically perceive streaks as beginning after the
third success (or failure) at minimum (Carlson and Shu 2007), I focus on
streaks of three round wins.\footnote{Three happens to also be a
  reasonable number for series that lasts at maximum 11 rounds.} Table
\ref{tbl:cod-round-win-prop-after-k-wins} shows \(P^{w,kr}\) and
\(P^{l,kr}\) for round win rate and loss rate following \(k = 3\) round
win streaks respectively.

\begin{longtable}{rrrrrrr}
\caption{First, observed proportion of wins ($\hat{P}^{kr,\text{win}}_O$) and expected proportion of wins, both un-adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$), after 3-round win streak, for a series lasting $r$ rounds. Second, observed proportion of losses ($\hat{P}^{kr,\text{loss}}_O$) and expected proportion of losses, both un-adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$), after 3-round loss streak}\label{tbl:cod-round-win-prop-after-k-wins} \\
\toprule
\multicolumn{7}{c}{\text{3 round win streak}} \\
$r$ & $N^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$ & $\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$ \\ 
\midrule
7 & 209 & $75\%$ & $75\%$ (0.58) & $61\%$ (<=0.01) \\
8 & 209 & $62\%$ & $60\%$ (0.28) & $45\%$ (<=0.01) \\
9 & 193 & $52\%$ & $50\%$ (0.33) & $35\%$ (<=0.01) \\
10 & 151 & $44\%$ & $43\%$ (0.45) & $29\%$ (<=0.01) \\
11 & 150 & $40\%$ & $38\%$ (0.29) & $25\%$ (<=0.01) \\
\toprule
\multicolumn{7}{c}{\text{3 round loss streak}} \\
$r$ & $N^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$ & $\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$ \\ 
\midrule
10 & 60 & $13\%$ & $14\%$ (0.64) & $10\%$ (0.26) \\ 
11 & 129 & $24\%$ & $25\%$ (0.63) & $16\%$ (<=0.01) \\ 
\bottomrule
\end{longtable}

@@

\leavevmode\vadjust pre{\hypertarget{ref-vafa2017}{}}%
Vafa, Keyon. 2017. {``Is the Hot Hand Fallacy a Fallacy?''}
\url{https://keyonvafa.github.io/hot-hand/}.
